Value Ordering, Discrepancies, and Restarts for Subgraph Isomorphism

### 2017-12-13 paper/paper.tex
More things

\definecolor{inferno7}{rgb}{0.976471, 0.584314, 0.039216}

@@

\begin{abstract}
    Modern subgraph isomorphism solvers use value-ordering heuristics to direct a constraint
    programming style search. These heuristics are not perfect, particularly for early branching
    choices. We show that discrepancy-based searches are too expensive to be effective in this
    setting.  However, using restarts with a random value-ordering heuristic beats conventional
    search with the best tailored heuristic.  This motivates the introduction of a slightly-random
    value-ordering heuristic with similar behaviour to the tailored heuristic: when combined with
    restarts, this new search strategy is even more effective on satisfiable instances, whilst not
    significantly decreasing performance on unsatisfiable instances.
\end{abstract}

@@

?? Subgraph isomorphism is useful.

The current single strongest subgraph isomorphism solver uses ``highest degree first'' as a
value-ordering heuristic \citep{dblp:conf/cp/McCreeshP15,dblp:conf/ijcai/McCreeshPT16}.  This is
much better than not having a value-ordering heuristic at all, but it is far from perfect,
particularly for early branching choices. There are two reasons to suspect a better option may
possible.  Firstly, even if degree were a perfect source of information, many graphs do not have a
large degree distribution, and so we would still need to determine \emph{which} vertex of highest
degree would be best.  Secondly, experiments with a parallel search strategy which explicitly steals
early branching choices often gives strongly super-linear speedups on satisfiable instances
\citep{dblp:conf/cp/McCreeshP15}.

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search (which perform poorly), and restarts (which are
extremely beneficial). To make restarts work, we introduce a new value-ordering heuristic, which is
nearly the same as ``highest degree first'' except with small amounts of heavily biased randomness.
The effects of the changes we propose are shown in \cref{figure:scatter-by-family}: we can make a
state-of-the-art algorithm perform much better on a large number of satisfiable instances, whilst
performing worse only rarely on satisfiable instances, and never on unsatisfiable instances.
Further, these properties are \emph{not} shared by discrepancy searches (\cref{figure:scatter-dds})
or by random value-ordering with restarts (\cref{figure:scatter-random}).

@@

@@

\newcommand{\siplabel}[1]{\label{line:sip:#1}}
\newcommand{\siplineref}[1]{line~\ref{line:sip:#1}}
\begin{algorithm}[p]\DontPrintSemicolon\small\SetInd{0.1em}{1em}
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (restart1sc) at ($(pic cs:restart1s) + (0, 0.15)$);
        \coordinate (restart1ec) at ($(pic cs:restart1e) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart1sc) (restart1ec)] { };
        \coordinate (restart2sc) at ($(pic cs:restart2s) + (0, 0.15)$);
        \coordinate (restart2ec) at ($(pic cs:restart2e) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart2sc) (restart2ec)] { };
        \coordinate (restart3sc) at ($(pic cs:restart3s) + (0, 0.15)$);
        \coordinate (restart3ec) at ($(pic cs:restart3e) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart3sc) (restart3ec)] { };
        \coordinate (restart4sc) at ($(pic cs:restart4s) + (0, 0.15)$);
        \coordinate (restart4ec) at ($(pic cs:restart4e) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart4sc) (restart4ec)] { };
        \coordinate (restart5sc) at ($(pic cs:restart5s) + (0, 0.15)$);
        \coordinate (restart5ec) at ($(pic cs:restart5e) - (0, 0.10)$);
        \coordinate (restart5rc) at ($(pic cs:restart5r) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart5sc) (restart5ec) (restart5rc)] { };
        \coordinate (restart6sc) at ($(pic cs:restart6s) + (0, 0.15)$);
        \coordinate (restart6ec) at ($(pic cs:restart6e) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart6sc) (restart6ec)] { };
        \coordinate (restart7sc) at ($(pic cs:restart7s) + (0, 0.15)$);
        \coordinate (restart7ec) at ($(pic cs:restart7e) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart7sc) (restart7ec)] { };
        \coordinate (restart8sc) at ($(pic cs:restart8s) + (0.05, 0.15)$);
        \coordinate (restart8ec) at ($(pic cs:restart8e) + (0, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart8sc) (restart8ec)] { };
        \coordinate (restart9sc) at ($(pic cs:restart9s) + (0, 0.15)$);
        \coordinate (restart9ec) at ($(pic cs:restart9e) + (-0.15, 0.00)$);
        \node [fill=inferno7, rounded corners, fit=(restart9sc) (restart9ec)] { };
    \end{tikzpicture}

@@

        \nl \tikzmark{restart1s}$\KwSty{global}~(R, R') \gets (0, 666 \times \textnormal{the next Luby value})$\tikzmark{restart1e} \;

@@

For the variable-ordering heuristic on \siplineref{variableordering} of \cref{algorithm:sip}, we use
smallest domain first, tiebreaking on highest degree. Variable ordering is not the focus of this
paper---as far as possible, we will leave it intact, so as not to affect the performance of the
algorithm on unsatisfiable instances.

For value ordering, which occurs on \siplineref{valueordering} of \cref{algorithm:sip}, we will
compare five strategies:

\paragraph{Random} We select a vertex dynamically at random (that is, we shuffle the vertices before
entering the $\KwSty{foreach}$ loop on \siplineref{valueordering} of \cref{algorithm:sip}). This is
\emph{usually} effectively equivalent to picking vertices in the order in which they appear in the
input files, although some instances from some benchmark suites are naturally in a special order
(which may or may not be a good order for searching).

\paragraph{Degree} We select vertices from highest degree to lowest degree. This is done by
permuting the target graph at the top of search. This heuristic is the current state of the art.

@@

\paragraph{Position-biased} We permute the graph at the top of search, as in the degree heuristic.
Then, as with the random heuristic, we shuffle the vertices before we enter the $\KwSty{foreach}$
loop. Instead of picking a vertex uniformly at random, we select select the first (that is, highest
degree) vertex with probability 0.5, the second vertex with probability 0.25, and the $n$th with
probability $2^{-n}$.  This heuristic heavily prefers vertices of high degree, similar to the
degree heuristic, but also introduces an element of randomness, and so can be used with restarts.

\paragraph{Degree-biased} Refining position-biased, we shuffle the vertices, using a weight of
$2^{\left|\neighbourhood(v)\right|}$ when deciding whether to branch on vertex $v$ next. (We cheat
slightly to avoid range issues with random number generation: we give the vertex with highest degree
in the entire graph weight $2^{50}$, and then give lower degree vertices smaller powers, giving
every vertex weight at least 1.  This is a bit of hack but programming is hard.) This heuristic
continues to prefer vertices of high degree, but will give the same chance of being selected next to
two vertices of equal degree.

@@

?? Dual Xeon E5-2697A v4 CPUs, 512GBytes RAM, running Ubuntu 17.04, implemented in C++ and compiled
using GCC 6.3.0. Our code is heavily based upon \citet{dblp:conf/cp/McCreeshP15}.

?? Deterministic RNG.

?? Bitsets.

?? The 5,725 instances \citep{dblp:conf/lion/KotthoffMS16}.

?? Other studies use a random selection of 200 of each of the mesh and images instances
\citep{DBLP:journals/cviu/DamiandSHJS11}, partly because some earlier solvers find many of these
instances extremely hard, and partly to avoid skewing a portfolio. We want larger numbers of
satisfiable instances, so we include all pattern / target pairs. This gives a total of 14,621
instances, at least 2,126 of which are known to be satisfiable, and at least 12,323 are
unsatisfiable.

?? Note that an awful lot of these instances are very easy. We are trying to tackle the remaining
hard satisfiable instances.

@@

    \caption{Cumulative number of instances solved over time, comparing our algorithm to other
    solvers. Below, zoomed in a bit ?? make this pretty.}
    \label{figure:others}
\end{figure}

?? In \cref{figure:others} we show that our solver is the bestest. For each algorithm, the $y$ value
gives the cumulative number of instances which (individually) can be solved in no more than $x$
milliseconds.  The vertical distance between two lines therefore shows how many more instances can
be solved by one solver than another, if every instance is run separately with the chosen $x$
timeout; the horizontal distance shows how many times longer the per-instance timeout would need to
be to allow the rightmost algorithm to succeed on $y$ out of the 14,621 instances (bearing in mind
that the two sets of $y$ instances solved by the two algorithms could be completely different).

?? These results show our algorithm clearly beating PathLAD and VF2, except for very low choices of
timeout. Our algorithm also beats Glasgow2 and Glasgow3, despite being slightly simpler---on an
instance by instance basis, sometimes the additional inference performed by these algorithms pays
off, but in aggregate, there is no difference for longer choices of timeout, and a clear gain for
shorter choices.

?? Add in SND if we can get it to run on the larger set of instances, maybe SAT just to have
something to cite showing how bad SAT is at this.

?? Possibly also do induced, compare to Glasgow, LAD, PathLAD, VF2, VF3, McSplit.

    \caption{The cumulative number of instances solved over time, using the four different
    value-ordering heuristics.}
    \label{figure:value-ordering-heuristics}
\end{figure}

    \caption{An instance by instance comparison of the degree and degree-biased heuristics.}
    \label{figure:scatter-heuristics}
\end{figure}

    \caption{The effects of using depth-bounded discrepancy search.}\label{figure:scatter-dds}
\end{figure}

The performance of both of the biased heuristics and the degree heuristic are very similar: the
degree-biased heuristic has slightly worse performance below a 100s timeout, and effectively equal
performance above it. This shows that we can introduce an element of randomness into the degree
value-ordering heuristic without adversely affecting its performance \emph{in aggregate}.
\Cref{figure:scatter-heuristics} gives a more detailed look at these results. In this plot,
satisfiable and unsatisfiable instances are shown using coloured shapes and black dots respectively.
On the $x$-axis we measure the degree heuristic, whilst on the $y$-axis we measure the degree-biased
heuristic. Points on the outer axes represent instances which timed out with one heuristic but not
the other.  This plot shows that despite the aggregate performance being very similar, on an case by
case basis, the two heuristics can make a large difference to the performance of satisfiable
instances.

@@

?? Quick intro to discrepancy search
\citep{DBLP:conf/ijcai/HarveyG95,DBLP:conf/aaai/Korf96,DBLP:conf/ijcai/Walsh97,DBLP:conf/cpaior/KarouiHLN07,DBLP:journals/jea/ProsserU11}.
Discrepancy search is about value ordering.

@@

@@

    \caption{Cumulative number of instances solved over time, with (dotted lines) and without (solid
    lines) restarts, and with depth-bounded discrepancy search (dashed line).}
    \label{figure:restarts}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-random.pdf}
    \caption{Instance by instance comparison of the basic algorithm with the degree heuristic,
    versus random value-ordering with restarts.}
    \label{figure:scatter-random}
\end{figure}

@@

    \caption{Instance by instance comparison of the basic algorithm with the degree heuristic,
    versus degree-biased value ordering with restarts.}
    \label{figure:scatter-by-family}
\end{figure}

@@

@@

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-parallel.pdf}

    \caption{Parallel}
    \label{figure:scatter-parallel}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-final.pdf}

    \caption{Final results}
    \label{figure:final}
\end{figure}

?? Parallel

@@

\appendix
\clearpage
\section{Further Experiments}

?? engineering aspects: look at what happens without nogoods in \cref{figure:scatter-nogoods}, and
at performance with restarts on degree in \cref{figure:scatter-overheads}.

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-scatter-nogoods.pdf}

    \caption{Is nogood recording important?}
    \label{figure:scatter-nogoods}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-scatter-overheads.pdf}

    \caption{Is nogood recording expensive?}
    \label{figure:scatter-overheads}
\end{figure}

?? effects of restart policies, \cref{figure:restart-policies}.

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-restart-policies.pdf}

    \caption{Different restart policies.}
    \label{figure:restart-policies}
\end{figure}

>>>>

\definecolor{highlight}{rgb}{0.819608, 0.733333, 0.34902}

@@

\begin{abstract}
    Modern subgraph isomorphism solvers use value-ordering heuristics to direct a constraint
    programming style search. These heuristics are far from perfect, and experiments show that using
    a random value-ordering heuristic with restarts beats conventional search with the best known
    tailored heuristic. This motivates the introduction of a slightly-random value-ordering
    heuristic with similar behaviour to the tailored heuristic: when combined with restarts, this
    new search strategy is over a hundred times more effective on satisfiable instances, and does
    not significantly decrease performance on unsatisfiable instances. In contrast,
    discrepancy-based searches are too expensive to be effective in this setting.
\end{abstract}

@@

The subgraph isomorphism problem is to find a copy of a small ``pattern'' graph inside a larger
``target'' graph.  The current single strongest subgraph isomorphism solver uses ``highest degree
first'' as a value-ordering heuristic to direct a constraint programming style search
\citep{DBLP:conf/cp/McCreeshP15,DBLP:conf/lion/KotthoffMS16,DBLP:conf/ijcai/McCreeshPT16}.  This is
much better than not having a value-ordering heuristic at all, but it is far from perfect,
particularly for early branching choices. There are two reasons to suspect a better option may
possible.  Firstly, even if degree were a perfect source of information, many target graphs do not
have a large degree distribution, and so we would still need to determine \emph{which} vertex of
highest degree would be best.  Secondly, experiments with a parallel search strategy which
explicitly steals early branching choices often gives strongly super-linear speedups on satisfiable
instances \citep{DBLP:conf/cp/McCreeshP15}.

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search (which performs poorly), and restarts (which are
extremely beneficial). To explore different parts of the search space when restarting, we introduce
a new value-ordering heuristic, which adds a small amount of randomness to the ``highest degree
first'' heuristic.  The effects of the changes we propose are shown in
\cref{figure:scatter-by-family}: we can make a state-of-the-art algorithm perform much better on a
large number of satisfiable instances, whilst performing worse only rarely on satisfiable instances,
and never on unsatisfiable instances.  Further, these properties are \emph{not} shared by
discrepancy searches (\cref{figure:scatter-dds}) or by random value-ordering with restarts
(\cref{figure:scatter-random}).

@@

?? Non-induced!

@@

\newcommand{\siplabel}[1]{\label{line:sip:#1}}
\newcommand{\siplineref}[1]{line~\ref{line:sip:#1}}
\begin{algorithm}[p]\DontPrintSemicolon\small\SetInd{0.1em}{1em}
    \begin{tikzpicture}[remember picture,overlay]
        \coordinate (restart1sc) at ($(pic cs:restart1s) + (0, 0.15)$);
        \coordinate (restart1ec) at ($(pic cs:restart1e) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart1sc) (restart1ec)] { };
        \coordinate (restart2sc) at ($(pic cs:restart2s) + (0, 0.15)$);
        \coordinate (restart2ec) at ($(pic cs:restart2e) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart2sc) (restart2ec)] { };
        \coordinate (restart3sc) at ($(pic cs:restart3s) + (0, 0.15)$);
        \coordinate (restart3ec) at ($(pic cs:restart3e) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart3sc) (restart3ec)] { };
        \coordinate (restart4sc) at ($(pic cs:restart4s) + (0, 0.15)$);
        \coordinate (restart4ec) at ($(pic cs:restart4e) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart4sc) (restart4ec)] { };
        \coordinate (restart5sc) at ($(pic cs:restart5s) + (0, 0.15)$);
        \coordinate (restart5ec) at ($(pic cs:restart5e) - (0, 0.10)$);
        \coordinate (restart5rc) at ($(pic cs:restart5r) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart5sc) (restart5ec) (restart5rc)] { };
        \coordinate (restart6sc) at ($(pic cs:restart6s) + (0, 0.15)$);
        \coordinate (restart6ec) at ($(pic cs:restart6e) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart6sc) (restart6ec)] { };
        \coordinate (restart7sc) at ($(pic cs:restart7s) + (0, 0.15)$);
        \coordinate (restart7ec) at ($(pic cs:restart7e) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart7sc) (restart7ec)] { };
        \coordinate (restart8sc) at ($(pic cs:restart8s) + (0.05, 0.15)$);
        \coordinate (restart8ec) at ($(pic cs:restart8e) + (0, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart8sc) (restart8ec)] { };
        \coordinate (restart9sc) at ($(pic cs:restart9s) + (0, 0.15)$);
        \coordinate (restart9ec) at ($(pic cs:restart9e) + (-0.15, 0.00)$);
        \node [fill=highlight, rounded corners, fit=(restart9sc) (restart9ec)] { };
    \end{tikzpicture}

@@

        \nl \tikzmark{restart1s}$\KwSty{global}~(R, R') \gets (0, \textnormal{the next restart sequence value})$\tikzmark{restart1e} \;

@@

For the variable-ordering heuristic on \siplineref{variableordering} of \cref{algorithm:sip}, we use
smallest domain first, tiebreaking on highest degree. Variable ordering is not the focus of this
paper---as far as possible, we will leave it intact, so as not to affect the performance of the
algorithm on unsatisfiable instances.  For value ordering, which occurs on
\siplineref{valueordering} of \cref{algorithm:sip}, we will compare four strategies:

\paragraph{Random} We select vertices uniformly at random.

\paragraph{Degree} We select vertices from highest degree to lowest degree. This heuristic is the
current state of the art.

@@

\paragraph{Biased} We branch by selecting a vertex $v'$ from the chosen domain $D_v$ with
probability \[ p(v') = \frac{2^{\deg(v')}}{\sum_{w \in D_v}{2^{\deg(w)}}} \text{.} \] This heuristic
continues to prefer vertices of high degree, but will give the same chance of being selected next to
two vertices of equal degree.  It also introduces an element of randomness, which is needed to make
restarts have an effect.

The biased heuristic resembles the well-known \emph{softmax} weighting scheme applied to the degree
heuristic, although usually \emph{softmax} uses a base of $e$ rather than $2$.  Experiments showed
that in this context, the choice of base is not important to the search space size; however, a base
of $2$ avoids the need to use floating point arithmetic, which was a substantial overhead.

@@

Our experiments are performed on systems with dual Intel Xeon E5-2697A v4 CPUs and 512GBytes RAM,
running Ubuntu 17.04. We implemented\footnote{Institutional DOI URL removed for anonymous review}
\cref{algorithm:sip} in C++ using the bit-parallel implementation of
\citet{DBLP:conf/aaai/HoffmannMR17} as a starting point, and compiled it using GCC 6.3.0. We use a
deterministic pseudo-random number generator for reproducibility.

We use the dataset introduced by \citet{DBLP:conf/lion/KotthoffMS16} for evaluation. This dataset
brings together a range of randomly-generated and application instance families from earlier papers.
Other studies use a random selection of 200 of each of the instances from the ``meshes'' and
``images'' families \citep{DBLP:journals/cviu/DamiandSHJS11} because some earlier solvers find many
of these instances extremely hard. We would like to have a larger number of satisfiable instances in
our test set, and so we include all pattern / target pairs. This gives a total of 14,621 instances
(rather than the original 5,725). At least ?? of these instances are known to be satisfiable, and at
least ?? are unsatisfiable.

@@

    \caption{Above, the cumulative number of instances solved over time, comparing our algorithm
    (both in its basic form, and with the improvements introduced in the remainder of the paper) to
    other solvers. Below, the same, looking only at satisfiable instances.}
    \label{figure:others}
\end{figure}

We begin by verifying that our implementation of the basic \cref{algorithm:sip} is competitive. In
\cref{figure:others} we show the cumulative number of instances solved over time, using our
implementation (both with the degree heuristic, and with the modifications described in the
remainder of this paper), the Glasgow2 and Glasgow3 algorithms from which \cref{algorithm:sip} is derived
\citep{DBLP:conf/cp/McCreeshP15,DBLP:conf/lion/KotthoffMS16}, the PathLAD variation of the LAD
algorithm \citep{DBLP:journals/ai/Solnon10,DBLP:conf/lion/KotthoffMS16}, and VF2
\citep{DBLP:journals/pami/CordellaFSV04}. For each algorithm, the $y$ value
gives the cumulative number of instances which (individually) can be solved in no more than $x$
milliseconds.  The vertical distance between two lines therefore shows how many more instances can
be solved by one solver than another, if every instance is run separately with the chosen $x$
timeout; the horizontal distance shows how many times longer the per-instance timeout would need to
be to allow the rightmost algorithm to succeed on $y$ out of the 14,621 instances (bearing in mind
that the two sets of $y$ instances solved by the two algorithms could be completely different).

As expected, the performance of \cref{algorithm:sip} with the degree heuristic is very close to that
of Glasgow2, although we perform better at lower runtimes because we use simpler preprocessing at
the top of search. Our implementation also clearly beats PathLAD and VF2, except for very low
choices of timeout.

The dataset includes many instances which are extremely easy for a good solver, and so it can be
hard to see the differences between the stronger solvers at higher runtimes. This paper focusses
upon improving the performance on the remaining hard satisfiable instances, and so in the second
plot in \cref{figure:others} (and in subsequent cumulative plots) we show only satisfiable
instances, and use a reduced range on both axes.

@@

?? Quick intro to discrepancy search
\citep{DBLP:conf/ijcai/HarveyG95,DBLP:conf/aaai/Korf96,DBLP:conf/ijcai/Walsh97,DBLP:conf/cpaior/KarouiHLN07,DBLP:journals/jea/ProsserU11}.
Discrepancy search is about value ordering, and it mostly looks at optimisation problems and at
problems where an optimality proof is not needed.

@@

    \caption{Comparing depth-bounded discrepancy search to backtracking search, both with the degree
    heuristic.}\label{figure:scatter-dds}
\end{figure}

    \caption{The cumulative number of satisfiable instances solved over time, using four
    different value-ordering heuristics. The degree and biased lines are close together.}
    \label{figure:value-ordering-heuristics}
\end{figure}

    \caption{An instance by instance comparison of the degree and biased heuristics on all
    instances. Points on the outer axes are timeouts, and point style shows instance family.}
    \label{figure:scatter-heuristics}
\end{figure}

The performance of the two degree heuristics are very similar: the
biased heuristic has slightly worse performance below a 100s timeout, and effectively equal
performance above it. This shows that we can introduce an element of randomness into the degree
value-ordering heuristic without adversely affecting its performance \emph{in aggregate}.
\Cref{figure:scatter-heuristics} gives a more detailed look at these results. In this plot,
satisfiable and unsatisfiable instances are shown using coloured shapes and black dots respectively.
On the $x$-axis we measure the degree heuristic, whilst on the $y$-axis we measure the biased
heuristic. Points on the outer axes represent instances which timed out with one heuristic but not
the other.  This plot shows that despite the aggregate performance being very similar, on an case by
case basis, the two heuristics can make a large difference to the performance of satisfiable
instances.

@@

    \caption{The cumulative number of satisfiable instances solved over time, with and without
    restarts.}
    \label{figure:restarts}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-random.pdf}
    \caption{Comparing basic backtracking with the degree heuristic, versus the Random heuristic
    with restarts.}
    \label{figure:scatter-random}
\end{figure}

@@

    \caption{Comparing basic backtracking with the degree heuristic, versus the biased
    heuristic with restarts.}
    \label{figure:scatter-by-family}
\end{figure}

@@

?? Justify aggregate speedups on sat instances

\subsection{Further Experiments}

\begin{itemize}
    \item The choice of Luby multiplier is not hugely important, although 100 is too small and 1,000
        is too big.
    \item The base of the exponential does not have to be $e$, and it may be easier on implementers
        to use 2. Using a polynomial weighting is bad, and using a base of $|D_v|$ is bad.
    \item Using geometric restarts instead of Luby does not give much of a benefit. A constant
        restart policy is also fine (and terminates on unsatisfiable instances because we count
        backtracks).
    \item Using rank with restarts is better than random with restarts, but not as good as using
        biased with restarts.
    \item Nogood recording is important.
    \item Nogood recording is cheap.
    \item Discarding subsumed nogoods may be done cheaply, if memory space is a concern.
\end{itemize}

@@

?? No theoretical justification for biased. Also tried polynomial weightings, exponential using
$\left|D_v\right|$ as the base. Using $e$ (or for that matter, $2$ or $\pi$) as a base seems to be
``just the right amount'' of randomness.

@@

?? Parallel future work

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-as.pdf}
    \caption{?? Aggregate speedups on satisfiable instances}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-degree.pdf}

    \caption{When is the degree heuristic good?}
    \label{figure:scatter-degree}
\end{figure}

@@
